Stat 400 Presentation

### 2021-12-09 Stat 400 presentation.Rmd
typo's

- The goal of the study is to generate epidemiological based on natural mechanism of transmission of this disease assuming random interactions of a large-finite number of individuals in very short distance ranges.

@@

- This is approached through an SIR model: Susceptible, Infected, Recovered. All change based on time as the function iterates through a set number of days. 
  - 0.5% of the initial subjects start out with the virus (infected)
  - 99.5% subjects are susceptible
  - 0% recovered

## Variables

- Factors to consider in the transmission of a virus. 
  - What is the relationship and distribution between the infection probability and the physical distance
  - High/low virus load, varying physical distances, ineffective vs effective mask wearing. 
  - Environmental conditions: humidity, temperature, air ventilation. 
- Based on real epidemiological data analysis, these encompassing factors will be distributed Exponential(rate = lambda)
- Recovery and Incubation times ~ Gamma(alpha, beta), But in order to get whole number for days, we distribute them Possion(lambda)

>>>>

- The goal of the study is to generate epidemiological data based on the natural mechanism's of transmission of the virus assuming random interactions of a large-finite number of individuals in very short distance ranges.

@@

- This is approached through an SIR model: Susceptible, Infected, Recovered. All change in the SIR model is based on time, as the function iterates through a set number of days. 
  - 0.5% of the initial subjects start out with the virus (infected)
  - 99.5% subjects are susceptible.
  - 0% starting recovery.

## Variables and Distributions

- Factors to consider in the transmission of a virus. 
  - What is the relationship and distribution between the infection probability and the physical distance?
  - High/low virus load, varying physical distances, ineffective vs effective mask wearing. 
  - Environmental conditions: humidity, temperature, air ventilation. 
- Based on real epidemiological data analysis, these encompassing factors will be distributed Exponential(rate = lambda)
- Recovery and Incubation times ~ Gamma(alpha, beta), But in order to get whole number for our outputted days, we chose to distribute them Possion(lambda)
